better title eventually

### 2015-05-11 cs261n-paper/paper.tex
wrapped up design section

%\documentclass{article}
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}

@@

\section{UX sprint} 
\indent \indent Talk about it just enough that it makes a good storyline for the experiment that we 
are proposing a design of. Motivate it a little bit, and tell a story. Then refer to the 
Appendix for additional information.

@@

\subsection{WHAT IS THIS}

\noindent {\bfseries Motivation and Background Story} talk about the generalizability of the work, what we aim to find, and what future work this will lead to. Be sure to sketch the storyline of honing in on specific features.

@@

\subsection{Overview}
\indent \indent For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both. There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use. The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.

We start off the experiment by telling them that they are in an adversarial setting, and that some websites are blocked and some websites are not. We will instruct them to visit notblocked.com and also blocked.com to illustrate the situation that they are in. We will also explain what Tor is, and how they can use it if necessary, and ask them to complete the set of tasks. To complete all the tasks, the participants will ultimately need to get the correct configuration settings for the country they are simulated to be in. We will end the experiment with a survey which asks them things like their security background, tech exposure, what was unexpected, what was hard, etc. We plan to analyze: which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.

@@

We plant to present our work at HotPETS2015 and solicit feedback on the design 
of this experiment. Specifically, we would want a reliable way to target the testing of 
specific transports. But given that the average user would not have domain knowledge of 
what transports are for Tor, is there anything to infer from participants' selection of transports, 
or do we assume they are trying transports at random?

@@

We plan to present our work at HotPETS2015 and solicit feedback on the design
of this experiment. Circumvention is broader than the stereotypical ``dissident blogger'' 
use case. We will solicit feedback on which additional tasks will provide additional insight,
or if there are different tasks which are representative of other censorship evasion use cases.

@@

\indent \indent Talk about the two-pronged qualitative and empirical data measurement stuff here.

\subsection{Qualitative Data} 
Write about the exit survey here. Write down number of questions, surveygizmo, etc.

\subsection{Empirical Data} 
Screen capture, timing, completion, clicks, etc. Things to measure about the activity.

@@

\section{Future Work}
And any work that needs to be done for the experiment. Give a brief timeline.

Next stps to take after the experiment, can also be here. %is this too far away?

@@

\section{UX sprint} 
Details. Gory gory details of how it all went down. 
Include the recruitment process, the setup, what the exact 
tasks were for participants, demographics, everything. 
It all should have a home here.

@@

>>>>

%\documentclass{article}
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}

@@

\section{UX sprint} 
\indent \indent Talk about it just enough that it makes a good storyline for the experiment that we 
are proposing a design of. Motivate it a little bit, and tell a story.

Appendix ~\ref{sec:pilot}.

@@

\subsection{Motivation}
 talk about the generalizability of the work, what we aim to find, and what future work this will lead to. Be sure to sketch the storyline of honing in on specific features.

@@

\subsection{What is Required of Users}
\indent \indent For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both. There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use. The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.

@@

We plant to solicit feedback on the design of this experiment at HotPETS2015.
Specifically, we would want a reliable way to target the testing of 
specific transports. But given that the average user would not have domain knowledge of 
what transports are for Tor, is there anything to infer from participants' selection of transports, 
or do we assume they are trying transports at random?

@@

We plant to solicit feedback on the design of this experiment at HotPETS2015. 
Circumvention is broader than the stereotypical ``dissident blogger'' 
use case. We will solicit feedback on which additional tasks will provide additional insight,
or if there are different tasks which are representative of other censorship evasion use cases.

@@

\indent \indent Our experiment consists of three parts: informing and motivating the participants in order 
to roleplay in the experiment, asking our participants to complete a set of web browsing tasks which will 
require them to circumvent censorship using the Tor Browser, and soliciting feedback from our participants
about their experience. With participants' consent, we will also record their computer screen to monitor 
their activity and employ a browser extension to take empirical measurements (such as idle waiting time, 
how fast a particular task was completed, etc.) throughout the duration of this experiment.

Each session of 30 participants will be placed in the same simulated censorship environment. 
We start off the experiment by informing our participants that they are in an adversarial setting, 
where some websites are blocked while other websites are not. We will instruct them to visit a censored
website and a non-censored website to illustrate that their devices and the network is fully functional and
operating as expected, but that they are in a censorship environment where some websites will fail to load. 
We will take a moment to explain what Tor is, how it is generally used in this case, and ask them to complete 
the aforementioned set of tasks. To complete all the tasks, the participants will ultimately need to get the correct
configuration settings for the country they are simulated to be in.

Then, each participant will be given about 30 minutes to complete their given Internet browsing tasks. 
Note that these Internet tasks themselves do not take very much time, but that the time is alloted in order
for participants to complete the configuration process. We believe that this is more than enough time to 
test the usability of the configuration process. Even if some participants may have succeeded with more 
time, we consider these cases to be a failure from a usability perspective as this would require too much
time from a user in the wild. Minimal interaction will be allowed with participants and the researchers. 
Researchers may inform participants of specific information (such as a bridge address) in a manner 
which does not disturb other participants (such as instructing users to visit a specific non-blocked website 
containing this information).

We will end the experiment with a survey of 17 questions in order to collect basic participation information, 
demographics of our participants, open-ended responses of their experience with censorship circumvention,
and general security questions to gauge their awareness in this area. Along with the empirical measurements 
we have taken during the experiment, we will use this survey information to determine which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.

\subsection{Quantitative and Qualitative Data}   
\indent \indent We will collect quantitative and qualitative data from our participants after they have completed 
their Internet tasks. This will allow us to align user activity with which simulated censorship setting, 
correlate performance with any demographics, get an idea of participants' motivations.

The survey consists of 17 questions total, with a basic breakdown as follows. 
The complete list of survey questions can be found in Appendix ~\ref{sec:survey}.

%question breakdown
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item 2 session and participant information questions
\item 4 basic demographics questions
\item 5 questions regarding their experience
\item 2 technical calibration questions
\item 4 Internet attitude questions
\end{itemize}

We also take this time to and collect feedback on the experience as a whole and the usability of 
the Tor Browser. Out of the five questions, there are two multiple choice questions and three 
open-ended feedback questions in which our participants can write us any length of response. 
We opted for both concrete quantitative measurements of their experience along with free-text
qualitative data to gather a broad range of information from our 200 participants in a scalable manner.

\subsection{Empirical Data} 
Although quantitative and qualitative data provides valuable feedback into what users perceive of 
their censorship circumvention experience, it will be imperative that we check for the validity of their 
statements by analyzing empirical data collected by our browser extension during the process of the
experiment. Specifically, we will capture:

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item A participant's computer screen. 
\item Configuration dialog navigation. 
\item Keyboard and mouse activity.
\item Successfully visited websites. 
\item Unsuccessfully visited websites. 
\item Time to complete various tasks.
\end{itemize}

We hope that exploring correlations between a statement such as  ``I was frustrated it took so long'' 
with task completion time, how many times a user had to repeat a dialog, or other behaviors 
will be an illuminating process. These correlations may hint at what makes this configuration dialog 
usable or not usable for users.

Additionally, users are not always reliable not complete sources of feedback. We will use the 
empirical data to verify the validity of their statements (for instance, if a user was reportedly frustrated 
but completed the task in under a minute, we may enforce our own threshold for usability) as well as 
performing additional analyses independent from the collected qualitative data (such as separating time
idle from time spent typing during the completion of a task).

@@

\section{Future Work}
\indent \indent With the high-level design of the experiment complete and IRB approval  to conduct this
experiment,  the next steps are to implement the simulated censorship environments which participants 
will be placed in and to write the browser extension which will collect the empirical data. 
We wait on these tasks in order to incorporate the feedback on the design of this experiment 
we will receive at HotPETS2015, which will take place during July. We plan to conduct this study starting 
August 2015.

The goal of this experiment is to measure how usable Tor Browser is as a censorship circumvention
tool. We hope that this experiment will provide insight into what usability improvements can be made 
in order to better to make Tor Browser's advanced features more accessible to the average user. The results
of this experiment can be used to inform user interaction designs which will result in shorter configuration
completion time and more reliable communication of the technical task to be completed, all while the 
this experience does not frustrate users from future use. We believe that experiments which perform
iterative A/B testing on various designs in order to increase usability to a wide, anonymous, international 
use base will be an interesting area of user interface design research while also making impacting changes
to a widely used censorship circumvention technology.

@@

\section{UX sprint} 
\label{sec:pilot}
Details. Gory gory details of how it all went down. 
Include the recruitment process, the setup, what the exact 
tasks were for participants, demographics, everything. 
It all should have a home here.

@@

\section{Exit Survey Questions}
\label{sec:survey} 
\indent \indent Our participants will be taking the following survey, hosted online at 
\url{http://www.surveygizmo.com/s3/2085559/Tor-Usability-Survey/SG_TEST_RUN}.\\

\noindent Recall that the survey consists of the following 17 questions, in this order: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item 2 session and participant information questions
\item 4 basic demographics questions
\item 6 questions regarding their experience with Tor
\item 2 technical calibration questions
\item 4 Internet attitude questions
\end{itemize}

\noindent Specifically, the questions are as follows: 
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item foo
\item bar
\item baz
\item foo
\item bar
\item baz
\item foo
\item bar
\item baz
\item foo
\item bar
\item baz
\item foo
\item bar
\item baz
\item foo
\item bar
\end{enumerate}
